\begin{abstract}
% Buildings in the United State consume 41\% of the total energy produced.
% In order to reduce the electrical footprint of buildings we present a new methodology to monitor building consumption and identify saving opportunities.
% The proposed method uncovers the relationships between the building's electrical devices and determines the devices normal behavior.
% Furthermore, by monitoring the devices relationships over time and comparing it to their usual relationships the misbehaving devices are automatically identified.
% We demonstrate that these misbehaviors correspond to incorrect usages of the devices thus sources of electricity wastes.
% The main challenge in this approach is to retrieve devices intrinsic-relationships from the sensor raw data.
% Indeed these relationships are hidden by noise and common trends inherent to all the sensors in the building.
% We overcome this issue by filtering the raw data using a recent signal processing technique: Empirical Mode Decomposition.
% The proposed method is evaluated with 18 weeks of data from two buildings located in U.S. and Japan.
% In spite of the national post-Fukushima measures to reduce the electricity consumption in Japan the proposed method found several saving opportunities in the Japanese dataset.
% In the other dataset it also detected several electricity wastes that account for up to 2500~kWh.

A typical medium-to-large building %($\geq 10^{5}$ square-feet) 
contains thousands of sensors, monitoring the HVAC system, lighting, and
other operational sub-systems.  With the increased push for operational efficiency,
operators are relying more on historical data processing to uncover opportunities for savings.  
However, they are overwhelmed 
with the deluge of data and seek more efficient ways to identify potential problems.  In this paper we present a new approach,
called the Strip and Bind Method (SBM), for uncovering potential problems in equipment behavior and in-concert usage.  SBM requires no a priori 
knowledge about the building and runs on all types of sensors -- treating each stream like a signal.
SBM uncovers relationships between devices and constructs a model for their in-concert usage.  It then flags deviations from the model as abnormal.

We run our system on a set of building sensor traces; each containing up to several thousand sensors and over 500 GB of data.
We demonstrate that, in many cases, these misbehaviors correspond to inefficient device usage that leads to energy waste.
% Since most sensors in the building are driven by the same underlying activity and weather patterns, we first had to remove
% the dominant trend to obtain the instrinstic behavioral pattern.  Detrending is done using 
% Empirical Mode Decomposition -- a recent signal processing tool.  We then construct a correlation-based model on the underlying 
% intrinsic signals. 
We evaluate our approach on 18 weeks of data from two buildings in different geographic locations and climates.
Energy waste is identified as high as 2500 kWh per device.
\end{abstract}
